Gametic Selection, Sex Ratio Bias, and Transitions Between Sex Determination Systems

### 2016-08-31 LaTeX/Turnover.tex
intro draft completed

@@

``Polygenic sex determination has been reported in many plants (e.g. Shannon \& Holsinger 2007), fishes (Vandeputte et al. 2007; Ser et al. 2010; Liew et al. 2012), crustaceans (e.g. Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
From Vuilleumier et al. 2007:
``Polymorphism for sex-determining genes within oramong populations has been reported in many speciesincluding houseflies, midges, woodlice, platyfish, cichlidfish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).

>>>>

Brief results summary.

@@

``Polygenic sex determination has been reported in many plants (e.g. Shannon \& Holsinger 2007), fishes (Vandeputte et al. 2007; Ser et al. 2010; Liew et al. 2012), crustaceans (e.g. Battaglia 1958; Battaglia \& Malesani 1959; Voordouw
\& Anholt 2002), bivalves (Haley 1977; Saavedra et al. 1997), gastropods (Yusa 2007a,b), and polychaetes (Bacci 1965, 1978; Premoli et al. 1996).''
From Vuilleumier et al. 2007:
``Polymorphism for sex-determining genes within or among populations has been reported in many species including houseflies, midges, woodlice, platyfish, cichlid fish, and frogs (Gordon, 1944; Kallman, 1970; Thomp-son, 1971; Macdonald, 1978; Bull, 1983; Rigaud et al., 1997; Caubet et al., 2000; Lande et al., 2001; Ogataet al., 2003; Lee et al., 2004; Mank et al., 2006).''
